---
output: github_document
editor_options: 
  chunk_output_type: console
---

[![Travis build status](https://travis-ci.org/mdsumner/NOmap.svg?branch=master)](https://travis-ci.org/mdsumner/NOmap)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/mdsumner/NOmap?branch=master&svg=true)](https://ci.appveyor.com/project/mdsumner/NOmap)
  [![Coverage status](https://codecov.io/gh/mdsumner/NOmap/branch/master/graph/badge.svg)](https://codecov.io/github/mdsumner/NOmap?branch=master)
[![CRAN status](https://www.r-pkg.org/badges/version/NOmap)](https://cran.r-project.org/package=NOmap)
 
 
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>",
  fig.path = "man/figures/README-", fig.height = 8, fig.width = 8, dpi = 300, out.width = "100%")

```

# NOmap 

The goal of NOmap is to make publication quality round Northern Ocean maps in polar projections with little effort. This package is COMPLETELY WIP AND WILL MAKE YOUR LIFE VERY BAD, DO NOT USE. 

```{r}
## see, you'll regret this
library(NOmap)
nmap <- NOmap(land = F)
data("wrld_simpl", package = "maptools")
wrld_simpl <- subset(wrld_simpl, !NAME %in% "Antarctica")
plot(nmap)
NOmap::SOplot(wrld_simpl, col = grey(0.6, alpha = 0.3))

library(trip)
SOplot(as(walrus818, "SpatialLinesDataFrame"), col = viridis::viridis(length(unique(walrus818$Deployment))))

```


Please note that the NOmap project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.
